---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "eespa11"
date: "11/sept/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Course Project

This is a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

Instructions:

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

## How to use the application
Using the data provided by the Galton Families data set, we fit a linear model to predict a child's height based on their gender and the average height of the parents.

The application is running at (https://eespa11.shinyapps.io/height/)

ui.R and Server.R Code in my github repository (https://github.com/eespa11/Course-Project-Shiny-Application-and-Reproducible-Pitch)

## Galton family data set

The data used in the app comes from the GaltonFamilies dataset.

```{r summary}
library (HistData)
data (GaltonFamilies)
summary (GaltonFamilies)
```

## Plot
The scatterplot below represents the data used for the prediction model
```{r plot}
library(HistData)
data(GaltonFamilies)
plot(jitter(GaltonFamilies$childHeight) ~ GaltonFamilies$midparentHeight,xlab="Average Height of the Parents (in inches)",ylab="Height of the Child (in inches)",main="Scatterplot of Galton Family Data",pch=19,frame.plot=FALSE,col=ifelse(GaltonFamilies$gender=="female", "red", "blue"))
legend(65,80,pch=c(19,19),col=c("red","blue"),c("female", "male"),bty="o",cex=.8)
```
